---
title: "0.0_what_is_an_island"
author: "Andrea Estandia"
date: "17/12/2020"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  github_document:
  toc: true
toc_depth: 4
editor_options:
chunk_output_type: console
---
  
```{r setup, echo=FALSE}
# Knitr settings: 
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
knitr::opts_chunk$set(
	echo = TRUE,
	message = TRUE,
	warning = TRUE
)
options(scipen = 999)
```

```{r, echo=FALSE}
source("./src/0.0_great-speciators_source.R")
```

Open a map with every piece of land as an individual polygon and select everything smaller than Madagascar
```{r}
land <-
  sf::st_read(dsn = file.path(data_path, "shapefiles/everythingisanisland.shp")) %>%
  mutate(area = st_area(.) / 1000000) %>% drop_units() %>% filter(area < 587000)
```

Open species distribution (requested from Birdlife)
```{r}
resident <-
  sf::st_read(dsn = file.path(data_path, "shapefiles/All_Species_Resident.shp"))
breeding <-
  sf::st_read(dsn = file.path(data_path, "shapefiles/All_Species_Breeding.shp"))
```

Calculate number of polygons in breeding and resident datasets
```{r}
breeding_npoly <- calculateNpolygon(breeding, land)
y = NULL
for (i in breeding_npoly) {
    tmp <- i %>% dplyr::select(SCINAME, npoly) %>%
      as.data.frame() %>%
      distinct(SCINAME, .keep_all = TRUE) %>%
      dplyr::select(-geometry)
    y <- rbind(y, tmp)
    breeding_npoly <- y %>% rename(species_name = SCINAME)
    breeding_npoly
}

resident_npoly <- calculateNpolygon(resident, land)
y = NULL
for (i in resident_npoly) {
    tmp <- i %>% dplyr::select(SCINAME, npoly) %>%
      as.data.frame() %>%
      distinct(SCINAME, .keep_all = TRUE) %>%
      dplyr::select(-geometry)
    y <- rbind(y, tmp)
    resident_npoly <- y %>% rename(species_name = SCINAME)
    resident_npoly
  }
npoly <- full_join(breeding_npoly, resident_npoly, by="species_name") %>% mutate(npoly=rowSums(cbind(npoly.x, npoly.y), na.rm = TRUE)) %>% dplyr::select(species_name, npoly)
write.csv(npoly, "npoly.csv", row.names = F)
```

```{r}
for (i in sp_distributions){
  assign("var", i)
npoly <- calculateNpolygon(i, land)
}

y = NULL
for (i in resident_npoly) {
    tmp <- i %>% dplyr::select(SCINAME, npoly) %>%
      as.data.frame() %>%
      distinct(SCINAME, .keep_all = TRUE) %>%
      dplyr::select(-geometry)
    y <- rbind(y, tmp)
    resident_npoly <- y %>% rename(species_name = SCINAME)
    resident_npoly
  }
```
Before doing anything else I need to add a "synonyms" column, adapting the current taxonomy for every species

List of species with different names are present if you filter the 'synonym' column and only keep values that don't match NA

Calculate mean, median, min, max and sd of 19 climatic variables for each species
```{r}
#Open bioclimatic variables
bio <- getData("worldclim", var = "bio", res = 2.5, path = file.path(data_path,"biovariables"))
alt <- getData("worldclim", var = "alt", res = 2.5, path = file.path(data_path,"biovariables"))

#Calculate intersection between species distribution and islands
calculateIntersect <- function(dataset, land) {
  out <- list()
  for (i in dataset$SCINAME) {
    out[[i]] <- dataset %>% filter(SCINAME==i) %>%
      st_buffer(dist = 0.0001, nQuadSegs = 1) %>%
      st_intersection(land, proj4string = "+init=epsg:4326") %>%
      st_cast("MULTIPOLYGON") %>%
      st_cast("POLYGON")
  }
  out
}

resident_npoly <- calculateIntersect(resident, land)

##Remove those list objects that are empty (e.g. seabirds that haven't intersected with an island)
resident_npoly_complete <- list()
for (i in resident_npoly){
  if(length(i$OBJECTID)>0){
    resident_npoly_complete[[as.character(unique(i$SCINAME))]] <- i
  }
}

#19 WorldClim Biovariables
list_biovar <- as.list(bio)

datalist = list()
for (var in list_biovar){
  var_name <- var@data@names
  datalist[[as.character(var_name)]]  <- calculateBioclimate(resident_npoly_complete, var)
}
biovariables = plyr::join_all(datalist[1:19])

#Altitude

altitude <- calculateBioclimate(resident_npoly_complete, alt)

 ##These species are not present in the main dataset because their taxonomy is complicated so re-do with this names
list_outliers <- c("Hypotaenidia philippensis","Todiramphus chloris","Pericrocotus flammeus","Kittacincla malabarica","Pardaliparus elegans","Artamus leucoryn","Chalcites minutillus","Heleia squamiceps","Poliolophus urostictus","Edolisoma coerulescens","Pachycephala pectoralis","Pellorneum ruficeps","Hirundapus cochinchinensis","Nesoenas picturatus","Malacocincla abbotti","Hypotaenidia torquata","Kittacincla luzoniensis","Charadrius mongolus","Heleia goodfellowi","Heleia javanica","Passerella iliaca","Fregata minor","Ceyx erithaca","Ramphiculus leclancheri","Microptilotis analogus","Melloria quoyi","Phaethon rubricauda","Leuconotopicus villosus","Calcarius lapponicus","Onychoprion anaethetus","Fratercula arctica","Porphyrio melanops","Erythrura cyaneovirens")

resident <- resident %>% filter(SCINAME %in% list_outliers)

resident_npoly_outliers <- calculateIntersect(resident, land)

npoly_outliers <- list()
for (i in resident_npoly_outliers){
  if(length(i$OBJECTID)>0){
    npoly_outliers[[as.character(unique(i$SCINAME))]] <- i
  }
}

#OR

npoly_outliers <- list()
for (i in resident_npoly_complete){
  if(unique(i$SCINAME) %in% list_outliers == TRUE){
    npoly_outliers[[as.character(unique(i$SCINAME))]] <- i
  }
}

list_biovar <- as.list(bio)

datalist = list()
for (var in list_biovar){
  var_name <- var@data@names
  datalist[[as.character(var_name)]]  <- calculateBioclimate(npoly_outliers, var)
}
biovariables = plyr::join_all(datalist[1:19])

```

Calculate maximum distance between furthest polygons
```{r}
resident_npoly_complete <- list()
for (i in resident_npoly){
  if(length(i$OBJECTID)>0){
    resident_npoly_complete[[as.character(unique(i$SCINAME))]] <- i
  }
}

#Dataset should be a list where all elements have at least one polygon. The list
#should be the intersection between the land and the distribution of the species

calculateMaxDistPoly <- function(dataset) {
  max=data.frame(matrix(ncol=1, nrow=1))
  colnames(max)<-"max_dist_poly"
  for (i in dataset) {
    tmp <- i %>%
      st_cast("MULTIPOLYGON") %>%
      st_cast("POLYGON", warn=F) %>%
      st_centroid() %>%
      st_distance() %>%
      max() %>%
      drop_units()
    max <- as.data.frame(rbind(max,tmp))
  }

  max <- max[-1,] %>% as.data.frame() %>% rename(max_dist_poly=".")
  max <- cbind(max,names(dataset)) %>%
    mutate(species_name=names(dataset)) %>%
    dplyr::select(max_dist_poly,species_name) %>%
    distinct(species_name, .keep_all = TRUE)
  max
}


calculateMedianDist <- function(dataset) {
  median=data.frame(matrix(ncol=1, nrow=1))
  colnames(median)<-"median_dist_poly"
  for (i in dataset) {
    tmp <- i %>% 
      st_cast("MULTIPOLYGON") %>%
      st_cast("POLYGON", warn=F) %>%
      st_centroid() %>%
      st_distance() %>%
      median() %>%
      drop_units()
    median <- as.data.frame(rbind(median,tmp))
  }
  
  median <- median[-1,] %>% as.data.frame() %>% rename(median_dist_poly=".")
  median <- cbind(median,names(dataset)) %>%
    mutate(species_name=names(dataset)) %>%
    dplyr::select(median_dist_poly,species_name) %>%
    distinct(species_name, .keep_all = TRUE)
  median
}

calculateSDdistances <- function(dataset) {
  sd=data.frame(matrix(ncol=1, nrow=1))
  colnames(sd)<-"sd_dist_poly"
  for (i in dataset) {
    tmp <- i %>% 
      st_cast("MULTIPOLYGON") %>%
      st_cast("POLYGON", warn=F) %>%
      st_centroid() %>%
      st_distance() %>%
      sd() 
    sd <- as.data.frame(rbind(sd,tmp))
  }
  
  sd <- sd[-1,] %>% as.data.frame() %>% rename(sd_dist_poly=".")
  sd <- cbind(sd,names(dataset)) %>%
    mutate(species_name=names(dataset)) %>%
    dplyr::select(sd_dist_poly,species_name) %>%
    distinct(species_name, .keep_all = TRUE)
  sd
}

calculateArea <- function(dataset) {
  area=data.frame(matrix(ncol=1, nrow=1))
  colnames(area)<-"area_dist_poly"
  for (i in dataset) {
    tmp <- i %>% 
      st_cast("MULTIPOLYGON") %>%
      st_cast("POLYGON", warn=F) %>%
      st_area(.)/1000000
    median <- as.data.frame(rbind(area,tmp))
  }
  
  area <- area[-1,] %>% as.data.frame() %>% rename(area_dist_poly=".")
  area <- cbind(area,names(dataset)) %>%
    mutate(species_name=names(dataset)) %>%
    dplyr::select(area_dist_poly,species_name) %>%
    distinct(species_name, .keep_all = TRUE)
  area
}


max_dist_poly <- calculateMaxDistPoly(max_dist_poly)
```

Combine the number of polygons occupied by the species with the expl variables datasets
```{r}
npolygons <- read_csv(file.path(data_path,"npoly/npoly.csv"))
checklist <- read_csv(file.path(data_path,"dfs/Clements-Checklist-v2019-August-2019.csv")) %>%  
  clean_names() %>% separate(scientific_name, c("genus", "species", "subspecies")) %>% 
  unite("species_name", c(genus,species), sep=" ") %>% dplyr::select(category, species_name, subspecies, range, family, order)
tip_rates <- read_csv(file.path(data_path,"dfs/tiprates.csv")) %>%  rename(species_name=name_pigot) %>%  separate(species_name, c("genus", "species")) %>% unite(species_name, c("genus", "species"), sep="_")
iucn <- read_csv(file.path(data_path,"dfs/Handbook of the Birds of the World and BirdLife International digital checklist of the birds of the world_Version_4.csv"))
hwi <- read_csv(file.path(data_path,"dfs/dataset_3.csv")) %>%  clean_names() 
traits1 <- read_csv(file.path(data_path,"dfs/dataset_2.csv")) %>% 
  clean_names() %>% 
  unite(species_name, c("genus", "species"), sep=" ")
traits2 <- read_csv(file.path(data_path,"dfs/dataset_1.csv")) %>% 
  clean_names() %>% 
  unite(species_name, c("genus", "species"), sep=" ") 
clim_var <- read_csv(file.path(data_path,"dfs/bioclimate.csv"))
clim_var2 <- read_csv(file.path(data_path,"dfs/bioclimate_outliers.csv"))
isolation <- read_csv(file.path(data_path,"dfs/isolation.csv"))
niche <-read_csv(file.path(data_path,"dfs/diet_realm_Pigot2020.csv")) %>% rename(species_name=tree_name) %>% 
  separate(species_name, c("genus", "species")) %>% unite(species_name, c("genus", "species"), sep=" ")
migr<- read_csv(file.path(data_path,"dfs/mig_beh.csv")) %>%  clean_names()
#############################################################

# dataset <- full_join(npolygons, checklist, by = "species_name") %>%
#   left_join(hwi, by="species_name") %>%
#   left_join(traits1, by = "species_name") %>% 
#   left_join(traits2, by = "species_name") %>%
#   left_join(iucn, by="species_name") %>% 
#   left_join(tip_rates, by="species_name") %>% 
#   clean_names() %>%
#   distinct(sort_v2019, .keep_all = TRUE)

###The new dataset below is the same one as the one above but the taxonomy has been reviewed

# dataset2 <- read_csv(file.path(data_path, "dataset_complete.csv")) %>% 
#   left_join(clim_var, by="species_name") %>% 
#   left_join(isolation, by ="species_name") %>% 
#   left_join(niche, by="species_name") %>% 
#   filter(islands==1) %>% 
#   group_by(species_name,category) %>% 
#   filter(category == "subspecies") %>% 
#   mutate(occurrences = n()) %>% 
#   filter(occurrences>1) %>% 
#   mutate(gs_estandia =   occurrences/log(npoly)) %>% 
#   mutate(gs_md =   occurrences/npoly) %>% 
#   arrange(desc(gs_index))
# dataset$gs_estandia <- stdize(dataset$gs_index, na.rm=T)

##Final dataset

dataset <- read_csv(file.path(data_path, "dfs/dataset_final.csv")) %>% separate(scientific_name, c("genus", "species", "subspecies")) %>% unite(species_name, c("genus", "species"), sep=" ")

dataset <- left_join(dataset, guys_final, by="tree_name")
guys_final <- guys_final %>% rename(tree_name=species_name) 
dataset_tiprates %>%
  ggplot(aes(x = netdiv,
             y = value))+
             # size=occurrences,
             #color=distr_index)) +
             geom_jitter(col = "#3ea6c2")
```

Intersectiong grid-species distribution
```{r}
grid <- sf::st_read(dsn = file.path(data_path,"shapefiles/ne_50m_graticules_1.shp"))
land <- sf::st_read(dsn = file.path(data_path,"shapefiles/ne_10m_land.shp"))

zlat <- sp1.3 %>%  filter(SCINAME=="Zosterops lateralis" | SCINAME=="Dulus dominicus")

alt <- getData("worldclim", var="alt", res=2.5, path =file.path(data_path,"biovariables"))
bio <- getData("worldclim", var="bio", res=2.5, path =file.path(data_path,"biovariables"))

calculateIntersect <- function(dataset, land) {
  out <- list()
  for (i in dataset$SCINAME) {
    out[[i]] <- dataset %>% filter(SCINAME==i) %>% 
      st_buffer(dist = 0.0001, nQuadSegs = 1) %>%
      st_intersection(land, proj4string = "+init=epsg:4326") %>%
      st_cast("MULTIPOLYGON") %>%
      st_cast("POLYGON") 
  }
  out
}

zlat_intersection <- calculateIntersect(zlat, land)
```

Load tree and select tips based on tree names we have
```{r}
p <- read.csv(file.path(data_path, "dfs/dataset_final.csv")) %>% filter(islands==1) %>% filter(gs_index<=4.3) %>% mutate(gs_md=occurrences/npoly)

p <- p %>% filter(tree_name!="NA") 

names <- as.character(unique(p$tree_name))


tree <- read.tree("/home/zoo/sjoh4959/Documents/programs/bamm-master/build/hackett.tre")

tree <- keep.tip(tree, names)

gs_estandia <- p$gs_estandia
names(gs_estandia) <- unique(p$tree_name)

#p <- p %>% distinct(tree_name, .keep_all = TRUE)
#matrix <- as.matrix(p$gs_estandia)
#rownames(matrix) <- p$tree_name

#Is there phylogenetics signal?
phylosignal <- phylosig(tree,matrix,test=TRUE, method="lambda")  
phylosignal

obj<-contMap(tree,gs_estandia)

plotTree.barplot(tree,matrix, tip.label=NULL)
dotTree(tree,p$gs_norm)
is.na(p$gs_norm)

clade_member <- clade.members.list(tree, tips = FALSE, tip.labels = TRUE)
clade_member

plot(obj, type="fan", show.tip.label=F)
arc.cladelabels(text="clade A",node=598)

plot(obj)

lastPP<-get("last_plot.phylo",envir=.PlotPhyloEnv)
xlim<-lastPP$x.lim
ylim<-lastPP$y.lim
plot(obj,xlim=xlim,ylim=ylim,ftype="off")
lastPP<-get("last_plot.phylo",envir=.PlotPhyloEnv)
tips <- c("Zosterops_lateralis", "Coracina_tenuirostris", "Nectarinia_aspasia",
          "Turdus_poliocephalus", "Accipiter_novaehollandiae", "Coereba_flaveola", "Hypothymis_azurea",
          "Tanysiptera_galatea", "Lalage_maculosa", "Petroica_multicolor", "Gallirallus_philippensis",
          "Certhidea_olivacea", "Dicaeum_trigonostigma", "Uria_aalge")

xpos<-lastPP$xx[sapply(tips,function(x,y) which(y==x),
                       y=obj$tree$tip.label)]
ypos<-lastPP$yy[sapply(tips,function(x,y) which(y==x),
                       y=obj$tree$tip.label)]
text(xpos,ypos,gsub("_"," ",tips),pos=4,font=0.5)
 


```

Calculations about GSI at the genus and family levels
```{r}
sp_genus1 <- dataset %>% 
  distinct(species_name, .keep_all = TRUE)  %>% 
  separate(species_name, c("genus", "species")) %>%
  group_by(genus) %>% 
  mutate(sp_in_genus = n()) %>% 
  distinct(genus, .keep_all = TRUE) %>% 
  dplyr::select(genus, sp_in_genus)

sp_genus2 <- dataset %>% 
  distinct(species_name, .keep_all = TRUE)  %>% 
  separate(species_name, c("genus", "species")) %>%
  group_by(genus) %>% 
  summarise(mean=mean(gs_estandia, na.rm=T), sd=sd(gs_estandia, na.rm=T), median=median(gs_estandia, na.rm=T))

sp_genus_total <- full_join(sp_genus1,sp_genus2,by="genus")


sp_family1 <- dataset %>% 
  distinct(species_name, .keep_all = TRUE)  %>% 
  group_by(family) %>% 
  mutate(sp_in_family = n()) %>% 
  distinct(family, .keep_all = TRUE) %>% 
  dplyr::select(family, sp_in_family)

sp_family2 <- dataset %>% 
  distinct(species_name, .keep_all = TRUE)  %>% 
  group_by(family) %>% 
  summarise(mean=mean(gs_estandia, na.rm=T), sd=sd(gs_estandia, na.rm=T), median=median(gs_estandia, na.rm=T))

sp_family_total <- full_join(sp_family1,sp_family2,by="family")

sp_family_total %>% 
  filter(sd!="NA") %>% 
  filter(sp_in_family>2) %>% 
  ggplot(aes(
    x=fct_reorder(family,median),
    y=median,
    size=sd
  ))+
  geom_jitter() +theme(
    plot.title = element_text(family = "Ubuntu", size=text_size),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.x = element_text(size= text_size, angle = 45, vjust = 0.9,hjust=1, face= "italic", family="Ubuntu"),
    axis.text.y = element_text(family="Ubuntu"),
    axis.title.x = element_text(family="Ubuntu"),
    axis.title.y = element_text(family="Ubuntu"),
    legend.position = "none",
    axis.ticks.y = element_blank()
  )
```

Plots
```{r}
dataset %>%
  filter(gs_norm >=0.5) %>% #| occurrences >= 7) %>%
  filter(occurrences>4) %>% 
  #filter(species_name!="Alcedo atthis") %>% 
  ggplot(aes(
    x = fct_reorder(species_name, gs_norm),
    y = gs_norm,
    size=npoly,
    #color=distr_index
  )) +
  geom_point(col="#3ea6c2")+
  scale_color_brewer(palette="Dark2")+
  geom_hline(yintercept=0.33, linetype="dashed", col= "darkgrey")+
  #geom_jitter(alpha = 0.2) +
  theme(
    plot.title = element_text(family = "Ubuntu", size=text_size),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.ticks.x = element_blank(),
    #axis.text.x = element_blank(),
    axis.text.x = element_text(size= text_size, angle = 45, vjust = 0.9,hjust=1, face= "italic", family="Ubuntu"),
    axis.text.y = element_text(family="Ubuntu"),
    axis.title.x = element_text(family="Ubuntu"),
    axis.title.y = element_text(family="Ubuntu"),
    axis.ticks.y = element_blank()) + labs(y = "Great Speciator Index\n", x= "\n", title="Great speciators (GSI > 0.33 regardless of # of subspecies or 7 subspecies or more)")

dataset %>%
  #filter(gs_norm >=0.4) %>% #| occurrences >= 7) %>%
  #filter(occurrences>4) %>% 
  #filter(species_name!="Alcedo atthis") %>% 
  ggplot(aes(
    x = range_size,
    y = isolation
    #color=distr_index
  )) +
  geom_point(col="#3ea6c2")+
  scale_color_brewer(palette="Dark2")+
  geom_hline(yintercept=0.33, linetype="dashed", col= "darkgrey")+
  #geom_jitter(alpha = 0.2) +
  theme(
    plot.title = element_text(family = "Ubuntu", size=text_size),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.ticks.x = element_blank(),
    #axis.text.x = element_blank(),
    axis.text.x = element_text(size= text_size, angle = 45, vjust = 0.9,hjust=1, face= "italic", family="Ubuntu"),
    axis.text.y = element_text(family="Ubuntu"),
    axis.title.x = element_text(family="Ubuntu"),
    axis.title.y = element_text(family="Ubuntu"),
    axis.ticks.y = element_blank()) 
 
p <- dataset %>% distinct(species_name, .keep_all = T) %>%
  filter(islands == 1) %>%
  ggplot(aes(x = occurrences, y = log(npoly))) +
  geom_jitter(col="#3ea6c2", alpha=0.7)+
  theme(
    plot.title = element_text(family = "Ubuntu", size=text_size),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.ticks.x = element_blank(),
    #axis.text.x = element_blank(),
    axis.text.x = element_text(size= text_size, angle = 45, vjust = 0.9,hjust=1, face= "italic", family="Ubuntu"),
    axis.text.y = element_text(family="Ubuntu"),
    axis.title.x = element_text(family="Ubuntu"),
    axis.title.y = element_text(family="Ubuntu"),
    axis.ticks.y = element_blank())+labs(y="log(# islands)", x="subspecies")
p

anim <- p +
  transition_time(gs_estandia, range=c(1,0))+shadow_mark()+ggtitle('Great Speciator Index = {frame_time}')

anim_save("first_saved_animation.gif", animation = anim, duration = 10, fps = 10, width = 900, height = 400, renderer = gifski_renderer())

```

```{r}
load("/home/zoo/sjoh4959/resident_npoly.RData")
world_poly <- resident_npoly
melanesia_poly <- resident_npoly
length(melanesia_poly)

melanesia_poly_complete <- list()
for (i in melanesia_poly){
  if(length(i$OBJECTID)>0){
    melanesia_poly_complete[[as.character(unique(i$SCINAME))]] <- i
  }
}

world_poly_complete <- list()
for (i in world_poly){
  if(length(i$OBJECTID)>0){
    world_poly_complete[[as.character(unique(i$SCINAME))]] <- i
  }
}


npoly_melanesia <- read_csv(file.path(data_path,"/npoly/npoly_melanesia.csv"))

melanesia <- read.csv(file.path(data_path, "dfs/melanesia_final.csv"))

npoly_world <- read_csv(file.path(data_path,"/npoly/npoly_world_complete.csv")) 

world <- read.csv(file.path(data_path, "dfs/dataset_final.csv"))

list_sp_missing_melanesia <- npoly_melanesia$species_name[!unique(npoly_melanesia$species_name) %in% unique(melanesia$species_name)]

list_sp_missing_world <- npoly_world$species_name[!unique(npoly_world$species_name) %in% unique(world$species_name)]

missing_melanesia <- npoly_melanesia %>% filter(species_name %in% list_sp_missing_melanesia) %>% left_join(checklist, by ="species_name") %>% left_join(hwi, by="species_name") %>%
   left_join(traits1, by = "species_name") %>% 
   left_join(traits2, by = "species_name") %>%
   left_join(iucn, by="species_name") %>% 
   left_join(tip_rates, by="species_name") %>% 
   clean_names() %>% left_join(niche, by="species_name") %>% dplyr::select(-temp_range, -annual_precip,-annual_temp)


melanesia_final <- full_join(melanesia, missing_melanesia) %>% unite(scientific_name, c("species_name","subspecies"), sep=" ") %>% distinct(scientific_name, .keep_all=TRUE) %>%separate(scientific_name, c("genus", "species", "subspecies"), sep=" ") %>% unite(species_name, c("genus","species"))  

missing_world <- npoly_world %>% filter(species_name %in% list_sp_missing_world) %>% left_join(checklist, by ="species_name") %>% left_join(hwi, by="species_name") %>%
   left_join(traits1, by = "species_name") %>% 
   left_join(traits2, by = "species_name") %>%
   left_join(iucn, by="species_name") %>% 
   left_join(tip_rates, by="species_name") %>% 
   clean_names() %>% left_join(niche, by="species_name") %>% dplyr::select(-temp_range, -annual_precip,-annual_temp)


missing_world <- full_join(world, missing_world) %>% unite(scientific_name, c("species_name","subspecies"), sep=" ") %>% distinct(scientific_name, .keep_all=TRUE) %>%separate(scientific_name, c("genus", "species", "subspecies")) %>% unite(species_name, c("genus","species"))  

write.csv(missing_world, "world_updated.csv", row.names = F)
```

```{r}
melanesia <- read_csv("/home/zoo/sjoh4959/Documents/projects/0.0_great-speciators/melanesia_updated.csv")
melanesia <- read_csv("/home/zoo/sjoh4959/Documents/projects/0.0_great-speciators/world_updated_2.csv")

melanesia_filtered<- melanesia %>% 
  filter(is.na(occurrences)) %>% 
  filter(category == "subspecies") %>% 
  filter(islands == 1) %>% 
  group_by(species_name) %>% 
  mutate(occurrences2 = n()) %>% 
  right_join(melanesia) %>% 
  mutate(nsubsp = coalesce(occurrences, occurrences2)) %>% 
  dplyr::select(-occurrences, -occurrences2)

write.csv(melanesia_filtered, "world_filtered.csv")

world_filtered <- read_csv("/home/zoo/sjoh4959/Documents/projects/0.0_great-speciators/world_filtered.csv") %>% 
  mutate(gs_md=nsubsp/npoly) %>% mutate(gs_estandia=nsubsp/log(npoly)) %>% left_join(migr, by ="species_name") %>% left_join(tip_rates, by="species_name") %>% mutate(div_rate=coalesce(netdiv.x, netdiv.y)) %>% dplyr::select(-netdiv.x,-netdiv.y)
world_filtered$gs_index <- stdize(world_filtered$gs_estandia, na.rm=T)
melanesia_filtered <- read_csv("/home/zoo/sjoh4959/Documents/projects/0.0_great-speciators/melanesia_filtered.csv") %>% 
  mutate(gs_md=nsubsp/npoly) %>% left_join(migr, by ="species_name") %>% left_join(tip_rates, by="species_name") %>% mutate(div_rate=coalesce(netdiv.x, netdiv.y)) %>% dplyr::select(-netdiv.x,-netdiv.y)

write.csv(melanesia_filtered, "melanesia_filtered3.csv", row.names = F)

melanesia_filtered %>%
  #filter(islands==1) %>% 
  #filter(category=="subspecies") %>% 
  #filter(gs_md <1) %>% 
  #filter(gs_estandia > 3) %>% 
  distinct(species_name,.keep_all = T) %>% 
  ggplot(aes(
    x = prec_wet_median,
    y = nsubsp
  )) +
  geom_jitter()+
  #scale_color_brewer(palette="Dark2")+
  geom_hline(yintercept=0.33, linetype="dashed", col= "darkgrey")+geom_smooth(method="loess")+
  #geom_jitter(alpha = 0.2) +
  theme(
    plot.title = element_text(family = "Ubuntu", size=text_size),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.ticks.x = element_blank(),
    #axis.text.x = element_blank(),
    axis.text.x = element_text(size= text_size, angle = 45, vjust = 0.9,hjust=1, face= "italic", family="Ubuntu"),
    axis.text.y = element_text(family="Ubuntu"),
    axis.title.x = element_text(family="Ubuntu"),
    axis.title.y = element_text(family="Ubuntu"),
    axis.ticks.y = element_blank()) 
 
melanesia_nsub <- world_filtered %>% dplyr::select(nsubsp)

hist(melanesia_filtered$nsubsp, breaks=25)

bioclim <- read_csv("/home/zoo/sjoh4959/bioclimate_melanesia2.csv") %>% separate(species_name, c("genus", "species")) %>% unite(species_name, c("genus", "species"), sep="_")

melanesia_filtered <- read_csv("/home/zoo/sjoh4959/Documents/projects/0.0_great-speciators/melanesia_filtered2.csv") %>% left_join(bioclim)

melanesia_filtered

```